%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------
    \cventry
    {Lead Communications Engineer} % Job title
    {BYU Spacecraft Group} % Organization
    {Provo, Utah} % Location
    {Apr. 2016 - PRESENT} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Twin satellites will fly in early 2018}
        \item {Design an end-to-end satellite communications system within technical constraints.}
        \item {RF engineering work designing antennas and amplifier systems.}
        \item {Developed Linux Address Family on-board satellite to support end to end communications}
        \item {Developed Ground Station system using an Ettus USRP and GNURadio}
        \item {Developed dishes and on-board antenna systems}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Assistant Systems Administrator} % Job title
    {BYU Computer Aided Engineering Design and Manufacturing} % Organization
    {Provo, Utah} % Location
    {Nov. 2015 - PRESENT} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Linux Infrastructure Engineer maintaining storage, authentication and user experience.}
        \item {Migrated to a new LDAP cluster and schema using SaltStack}
        \item {Implemented MIT Kerberos in the environment using SaltStack}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Systems Administrator} % Job title
    {SolvereOne and HouseCall IT} % Organization
    {Dulles, Virginia and Washington D.C.} % Location
    {Jun. 2013 - Oct. 2015} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintaining and designing secure network deployments.}
        \item {Deploying and maintaining Windows user and application systems.}
        \item {Catch-all Linux Administration}
        \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}
